Colourism in the East and South Asian Beauty Markets

### 2023-04-20 outputs/paper/paper.qmd
Update with model

#### Work space set-up ####
# Define required libraries 
library(lubridate)
library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)

@@

lightnessrange <- readr::read_csv(here::here("inputs/data/clean/lightnessrange.csv"), show_col_types = FALSE)
```

@@

#total number of shade range 
lightnessrange |>
  tabyl(group, light_range) |>
  adorn_totals("col")

@@

lightnessrange |>
  filter(group == 'India') |>
  ggplot(aes(x = brand, y = L)) +
    geom_dotplot(binaxis='y', 
               stackdir='center',
               binwidth = 0.7, 
               fill = "#ebb08a")  +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  coord_flip() +
  labs(
    y = "Lightness Value", 
    x = "Best Selling Indian Foundation Brands"
  )

@@

lightnessrange |>
  filter(group == 'Japan') |>
  ggplot(aes(x = brand, y = L)) +
    geom_dotplot(binaxis='y', 
               stackdir='center',
               binwidth = 0.5, 
               fill = "#e8b793") +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  coord_flip() +
  labs(
    y = "Lightness Value", 
    x = " Bestselling Japanese Foundation Brands"
  )

@@

#india & Japan

# lightnessrange |>
#   nrow()

lightnessrange |>
  ggplot(aes(x = light_range, fill = group)) +
  geom_bar() +
  theme_minimal() +
  labs(
    x = "Lightness Range",
    y = "Number of Foundation Shades"
  )

@@

lightnessrange |>
  filter(group == 'Japan') |>
  ggplot(aes(x = H, y = L)) +
    geom_point(fill = "#e8b793") +
  # scale_x_continuous(breaks=seq(22, 25, 0.1)) +
  theme_minimal() +
  labs(
    y = "Lightness Value", 
    x = "Hue"
  )

@@

install.packages("ggpubr")
install.packages("broom") 
install.packages("AICcmodavg")

library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(AICcmodavg)

one.way <- aov(group ~ L, data = lightnessrange)
summary(one.way)

>>>>

#### Work space set-up ####
# Define required libraries

library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)
library(ggalt)
library(broom)
library(kableExtra)

@@

lightnessrange <- readr::read_csv(here::here("inputs/data/clean/lightnessrange.csv"), show_col_types = FALSE)

brand_origin <- readr::read_csv(here::here("inputs/data/clean/brand_origin.csv"), show_col_types = FALSE)
```

@@

#total number of shade range 
brand_origin |>
  tabyl(group, light_range) |>
  adorn_totals("col")

@@

lightnessrange |>
  filter(group == 'India') |>
  ggplot(aes(light_range)) +
    geom_bar(aes(fill = brand)) +
  scale_y_continuous(breaks=seq(0, 30, 5)) +
  theme_minimal() +
  labs(
    y = "Number of Products", 
    x = "Lightness Range"
  )

@@

lightnessrange |>
  filter(group == 'Japan') |>
  ggplot(aes(light_range)) +
    geom_bar(aes(fill = brand)) +
  scale_y_continuous(breaks=seq(0, 50, 5)) +
  theme_minimal() +
  labs(
    y = "Number of Products", 
    x = "Lightness Range"
  )

@@

#Japan & India by domestic/international

brand_origin |>
  ggplot(aes(x = group, y = L, fill = origin)) +
    geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  labs(
    y = "Lightness Value", 
    x = "Country"
  )

@@

brand_origin |>
  ggplot(aes(x = S, y = L)) +
    geom_point() +
   geom_smooth(method="lm", se=FALSE) +
  scale_y_continuous(breaks=seq(0, 100, 10)) +
  scale_x_continuous(breaks=seq(0, 10, 0.10)) +
  theme_minimal() +
  labs(
    y = "Lightness", 
    x = "Saturation"
  )

@@

model <- lm(L ~ S, data = brand_origin)

summary <- tidy(model)

kbl(summary, caption = "Linear Regression Model Summary") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```{r}
ggplot(data, aes(x=S, y=L)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  labs(x="Saturation", y="Lightness")
